A Practical Guide for Generating Reproducible and Programmatic Neuroimaging Visualizations

### 2023-02-10 manuscript.Rmd
fig1 shift

---
title: A Practical Guide for Generating Reproducible and Programmatic Neuroimaging Visualizations
authors:
  - name: Sidhant Chopra
    thanks: Corresponding author
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
    email: sidhant.chopra@yale.com
  - name: Loïc Labache
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Elvisha Dhamala
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Edwina R Orchard
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Avram Holmes
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
keywords:
  - Neuroimaging visualization
  - Reproducibility 
  - Programmatic figures
  - Open Science
  - R
  - Python
  - Brain Visualization
abstract: Neuroimaging visualizations form the centerpiece of the interpretation and communication of scientific results, and are also a cornerstone for data quality control. Often, these images and figures are produced by manually changing settings on Graphical User Interfaces (GUIs). There now exist many well-documented code-based brain visualization tools that allow users to programmatically generate publication-ready figures directly within R, Python and MATLAB environments. Here, we provide a rationale for the wide-spread adoption of code-generated brain visualizations by highlighting corresponding advantages in replicability, flexibility, and integration over GUI based tools. We then provide a practical guide outlining the steps required to generate these code-based brain visualizations. We also present a comprehensive table of tools currently available for programmatic brain visualizations and provide didactic examples of visualizations and associated code as a point of reference. Finally, we provide a web-app (https://sidchop.shinyapps.io/braincode/) which can generate simple code-templates as starting points for these visualizations.
output: 
  bookdown::word_document2:
    toc: false
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    keep_tex: true
    latex_engine: lualatex
linestretch: 1.5
geometry: "left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}\onehalfspacing
- \usepackage[left]{lineno}
- \modulolinenumbers[5]
- \linenumbers
---

>>>>

---
title: A Practical Guide for Generating Reproducible and Programmatic Neuroimaging Visualizations
authors:
  - name: Sidhant Chopra
    thanks: Corresponding author
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
    email: sidhant.chopra@yale.com
  - name: Loïc Labache
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Elvisha Dhamala
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Edwina R Orchard
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Avram Holmes
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
keywords:
  - Neuroimaging visualization
  - Reproducibility 
  - Programmatic figures
  - Open Science
  - R
  - Python
  - Brain Visualization
abstract: Neuroimaging visualizations form the centerpiece of the interpretation and communication of scientific results, and are also a cornerstone for data quality control. Often, these images and figures are produced by manually changing settings on Graphical User Interfaces (GUIs). There now exist many well-documented code-based brain visualization tools that allow users to programmatically generate publication-ready figures directly within R, Python and MATLAB environments. Here, we provide a rationale for the wide-spread adoption of code-generated brain visualizations by highlighting corresponding advantages in replicability, flexibility, and integration over GUI based tools. We then provide a practical guide outlining the steps required to generate these code-based brain visualizations. We also present a comprehensive table of tools currently available for programmatic brain visualizations and provide didactic examples of visualizations and associated code as a point of reference. Finally, we provide a web-app (https://sidchop.shinyapps.io/braincode/) which can generate simple code-templates as starting points for these visualizations.
output: 
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    keep_tex: true
    latex_engine: lualatex
  bookdown::word_document2:
    toc: false
linestretch: 1.5
geometry: "left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}\onehalfspacing
- \usepackage[left]{lineno}
- \modulolinenumbers[5]
- \linenumbers
---
